Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-16 paper/paper.tex
ALG3's cost

  %Let $A^I$ be the cost of (extra-cluster) communication incurred in this phase by \TAlg between pairs that belonged to the single component at the end of the phase.
  %Let $A^E$ be the cost of (extra-cluster) communication incurred in this phase between the nodes that belong to different components at the end of this phase.
  Let $\TAlg(M)$ be the cost of migrations performed by \TAlg in this phase.
  During a single phase, it performs at most $2 \ell$ component merge operations, as
  exceeding this number means that a component of size $4$ exists, and the phase should have ended already.
  Combining this with Lemma~\ref{lem:1req} gives us $\TAlg(M) \leq 6\alpha\cdot\ell$.
  %Together with Lemma~\ref{lem:1req}, this allows us to bound the cost of migrations, $\TAlg(M) \leq 6\cdot\alpha\cdot\ell$.

  Now we bound $\TAlg(\sigma_I)$.
  Cluster of type $C_3$ contributes at most $(3 \alpha - 1)$ to $\TAlg(\sigma_I)$, as at most $2$ of pairs of nodes from the component are saturated and contribute $\alpha$ each, and the third, unsaturated pair contributes at most $\alpha-1$.
  Other cluster types contribute less: $C_1$ contributes $0$ and $C_2$ contributes $\alpha$.
  Summing this over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq \ell \cdot (3 \alpha-1) \leq 4\alpha\cdot\ell$.

>>>>

  %Let $A^I$ be the cost of (extra-cluster) communication incurred in this phase by \TAlg between pairs that belonged to the single component at the end of the phase.
  %Let $A^E$ be the cost of (extra-cluster) communication incurred in this phase between the nodes that belong to different components at the end of this phase.
  Let $\TAlg(M)$ be the cost of migrations performed by \TAlg in this phase.
  \TAlg performs at most $2 \ell$ component merge operations, as
  exceeding this number means that a component of size $4$ exists, and the phase should have ended already.
  Combining this with Lemma~\ref{lem:1req} gives us $\TAlg(M) \leq 6\alpha\cdot\ell$.
  %Together with Lemma~\ref{lem:1req}, this allows us to bound the cost of migrations, $\TAlg(M) \leq 6\cdot\alpha\cdot\ell$.

  Now we bound $\TAlg(\sigma_I)$.
  Cluster of type $C_3$ contributes at most $3 \alpha - 1$ to $\TAlg(\sigma_I)$, as $2$ of pairs of nodes from the component are saturated and contribute $\alpha$ each, and the third, unsaturated pair contributes at most $\alpha-1$.
  Other cluster types contribute less: $C_1$ contributes $0$ and $C_2$ contributes $\alpha$.
  Summing this over all $\ell$ clusters gives us $\TAlg(\sigma_I) \leq (3 \alpha-1)\cdot \ell \leq 4\alpha\cdot\ell$.
